Parsing Tweets into Universal Dependencies

### 2018-04-15 paper.tex
caption formatting; remove top and bottom rules on tables, as they don't really add anything

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2018}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage[scaled=.8]{beramono}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{tikz-dependency}
\usepackage{url}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage{subcaption}
\usepackage{arydshln}
\newcommand\BibTeX{B{\sc ib}\TeX}
\DeclareMathOperator*{\argmin}{argmin}
%\def\aclpaperid{214}
\aclfinalcopy
%%%%%%%
\usepackage{graphicx}
\newcommand{\heart}{\ensuremath\heartsuit}

@@

\paragraph{Non-syntactic tokens.}  
\begin{table}
\centering
\begin{tabular}{lrr}
\hline
\multicolumn{2}{r}{syntactic (\%)} & non-syntactic (\%)\\ \hline
emoticons & 0.25 & 0.95 \\
RT & 0.14 & 2.49\\
hashtag & 1.02 & 1.24 \\
URL & 0.67 & 2.38 \\
truncated words & 0.00 & 0.49 \\
 \hline
 total & 2.08 & 7.55 \\
 \hline
\end{tabular}
\caption{Proportions of non-syntactic tokens in our annotation. %\yicomment{should add also retweet at-mentions}
These statistics are obtained on 140 character-limited tweets. \label{tbl:non-synt-prop}}
\end{table}

@@

\subsubsection{Annotation Process}
\begin{table}
	\centering
	\begin{tabular}{rrrrr}
		\hline
		 & \multicolumn{2}{c}{\textsc{Tweebank v1}} & \multicolumn{2}{c}{\textsc{Tweebank v2}} \\
		split & tweets & tokens & tweets & tokens \\
		\hline
		train & 639 & 9,310 & 1,639 & 24,753 \\
		dev & --\hphantom{0} & --\hphantom{00} & 710 & 11,742 \\
		test & 201 & 2,839 & 1,201 & 19,112 \\
		\hline
		total & 840 & 12,149 & 3,550 & 55,607 \\
%		\textsc{v1} & tweets & 639 & 0 & 201 & 840 \\
%		& tokens  & 9,310 & 0 & 2,839 & 12149 \\
%		\hdashline
%		\textsc{v2} & tweets & 1,639 & 709 & 1,201 & 3,549 \\
%		 & tokens &	24,753	&	11,742	&	19,112 & 55,617\\
		\hline
	\end{tabular}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & $F_1$ \\
		\hline
		  Stanford CoreNLP & 97.3 \\
		 Twokenizer & 94.6 \\
% 		UDPipe v1.2 & 94.7 \\
		\hdashline
		UDPipe v1.2 & 97.4 \\
	 	our bi-LSTM tokenizer & 98.3 \\
		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}
%\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?}\yjcomment{it's a parsing work.}\nss{I guess I don't follow how parsing results 
%on combined training data affect our decision about how to tokenize.} trained 
%on the combination of the UD\_English and Singapore English dialect (Singlish) treebanks
%outperforms the one trained only on the dialect treebank.  
Our preliminary results
showed that our model trained on
the combination of UD\_English-EWT and \textsc{Tweebank v2}
outperformed the one trained only on the UD\_English-EWT or \textsc{Tweebank v2},
consistent with previous work on dialect treebank parsing \cite{wang-EtAl:2017:Long6}.
So we trained our tokenizer on the training portion of
\textsc{Tweebank v2} combined with the UD\_English-EWT training set
and tested on the \textsc{Tweebank v2} test set. % \yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}\yjcomment{add discussion}
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
 Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540} are rule-based systems and were not adapted
to the UD tokenization scheme.
The UDPipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system. Compared with UDPipe, we use an LSTM
instead of a GRU in our model and we also use a larger size for hidden units (64 vs.~20),
which has stronger representational power. 
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results speak to the value of statistical modeling
in tokenization for informal texts.%\nss{this paragraph needs copyediting}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it System & Precision\nss{Accuracy?} \\
		\hline
%		Stanford Postagger & 65.6 \\
		Stanford CoreNLP & 90.6 \\
%		UDPipe v1.2 & 78.7 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 93.7 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & 94.6 \\
		\hdashline
%		UDPipe v1.2 & 83.8 \\
		\citealp{ma-hovy:2016:P16-1} & 92.5 \\
%		our word bi-LSTM & 89.2 \\
%		our character + word bi-LSTMs & 91.5 \\
		\hline
	\end{tabular}
	\caption{POS tagger comparison on gold-standard tokens in the
          \textsc{Tweebank v2} test set. \label{tbl:pos-result}}
\end{table}

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
		\hline
		\it Tokenization System & $F_1$ \\
		\hline
		Stanford CoreNLP & 92.3 \\
		our bi-LSTM tokenizer (\S\ref{sec:tok}) & 93.3 \\
		\hline
	\end{tabular}
	\caption{\citet{owoputi-EtAl:2013:NAACL-HLT} POS tagging performance with automatic tokenization on
          the \textsc{Tweebank v2} test set. \label{tbl:pos-result-vs-tok}}
\end{table}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rccc}
		\hline
		\it System & UAS & LAS & Kt/s \\
		\hline
		\citet{kong-EtAl:2014:EMNLP2014} & 81.4 & 76.9 & 0.3 \\
		\citet{dozat-qi-manning:2017:K17-3} & 81.8 & 77.7 & 1.7 \\
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.2 & 75.7 & 2.3 \\
		\hdashline
		Ensemble (20) & 83.4 & 79.4 & 0.2 \\
		Distillation ($\alpha =1.0$) & 81.8 & 77.6 & 2.3 \\
		Distillation ($\alpha =0.9$) & 82.0 & 77.8 & 2.3 \\		
		Distillation w/ exploration & 82.1 & 77.9 & 2.3 \\
		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2} test set,
           with automatic POS tags. The ``Kt/s'' column shows
           the parsing speed evaluated by thousands of tokens
           the model processed per second.
            \label{tbl:parse-result}}
\end{table}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rrcc}
		\hline
		\it Pipeline stage & Score & Ours & SOTA \\
		\hline
		Tokenization  & \it $F_1$ & 98.3 & 97.3 \\		
		POS tagging &  \it  $F_1$ & 93.3 & 92.2 \\
		UD parsing & \it LAS $F_1$ & 74.0 & 71.4 \\
		\hline
	\end{tabular}
	\caption{Evaluating our pipeline against a state-of-the-art pipeline.\label{tbl:pipline} %\yicomment{see tab5 for our tokenizer the pos tagging number is 93.6, here is 93.7, should be consistent}
	}
\end{table}

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage[hyperref]{naaclhlt2018}
\usepackage{times}
\usepackage{latexsym}
\usepackage{amsmath}
\usepackage[scaled=.8]{beramono}
\usepackage[T1]{fontenc}
\usepackage[utf8x]{inputenc}
\usepackage{multirow}
\usepackage{xcolor}
\usepackage{tikz-dependency}
\usepackage{url}
\usepackage{multirow}
\usepackage{graphicx}
\usepackage[small,bf,skip=5pt]{caption}
\usepackage{subcaption}
\usepackage{arydshln}
\newcommand\BibTeX{B{\sc ib}\TeX}
\DeclareMathOperator*{\argmin}{argmin}
%\def\aclpaperid{214}
\aclfinalcopy
%%%%%%%
\usepackage{graphicx}
\newcommand{\heart}{\ensuremath\heartsuit}

@@

\paragraph{Non-syntactic tokens.}  
\begin{table}
\centering
\begin{tabular}{lrr}
%\hline
\multicolumn{2}{r}{syntactic (\%)} & non-syntactic (\%)\\ \hline
emoticons & 0.25 & 0.95 \\
RT & 0.14 & 2.49\\
hashtag & 1.02 & 1.24 \\
URL & 0.67 & 2.38 \\
truncated words & 0.00 & 0.49 \\
 \hline
 total & 2.08 & 7.55 \\
% \hline
\end{tabular}
\caption{Proportions of non-syntactic tokens in our annotation. %\yicomment{should add also retweet at-mentions}
These statistics are obtained on 140 character--limited tweets. \label{tbl:non-synt-prop}}
\end{table}

@@

\subsubsection{Annotation Process}
\begin{table}
	\centering
	\begin{tabular}{rrrrr}
%		\hline
		 & \multicolumn{2}{c}{\textsc{Tweebank v1}} & \multicolumn{2}{c}{\textsc{Tweebank v2}} \\
		split & tweets & tokens & tweets & tokens \\
		\hline
		train & 639 & 9,310 & 1,639 & 24,753 \\
		dev & --\hphantom{0} & --\hphantom{00} & 710 & 11,742 \\
		test & 201 & 2,839 & 1,201 & 19,112 \\
		\hline
		total & 840 & 12,149 & 3,550 & 55,607 \\
%		\textsc{v1} & tweets & 639 & 0 & 201 & 840 \\
%		& tokens  & 9,310 & 0 & 2,839 & 12149 \\
%		\hdashline
%		\textsc{v2} & tweets & 1,639 & 709 & 1,201 & 3,549 \\
%		 & tokens &	24,753	&	11,742	&	19,112 & 55,617\\
%		\hline
	\end{tabular}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
%		\hline
		\it System & $F_1$ \\
		\hline
		  Stanford CoreNLP & 97.3 \\
		 Twokenizer & 94.6 \\
% 		UDPipe v1.2 & 94.7 \\
		\hdashline
		UDPipe v1.2 & 97.4 \\
	 	our bi-LSTM tokenizer & 98.3 \\
%		\hline
	\end{tabular}
	\caption{Tokenizer comparison on the \textsc{Tweebank v2} test set.}\label{tbl:tok-result}
\end{table}
%\citet{wang-EtAl:2017:Long6} show that the parser\nss{tokenizer?}\yjcomment{it's a parsing work.}\nss{I guess I don't follow how parsing results 
%on combined training data affect our decision about how to tokenize.} trained 
%on the combination of the UD\_English and Singapore English dialect (Singlish) treebanks
%outperforms the one trained only on the dialect treebank.  
Our preliminary results
showed that our model trained on
the combination of UD\_English-EWT and \textsc{Tweebank v2}
outperformed the one trained only on the UD\_English-EWT or \textsc{Tweebank v2},
consistent with previous work on dialect treebank parsing \cite{wang-EtAl:2017:Long6}.
So we trained our tokenizer on the training portion of
\textsc{Tweebank v2} combined with the UD\_English-EWT training set
and tested on the \textsc{Tweebank v2} test set. % \yicomment{should mention that combination of corpora improves the results, otherwise we should answer why we didn't try training ONLY on Tweebank v2}\yjcomment{add discussion}
We report $F_1$ scores, combining precision and recall for token identification. Table \ref{tbl:tok-result} shows the
tokenization results, compared to  other available tokenizers. 
 Stanford CoreNLP \cite{manning-EtAl:2014:P14-5} and Twokenizer
\cite{ICWSM101540} are rule-based systems and were not adapted
to the UD tokenization scheme.
The UDPipe v1.2
\cite{straka-strakova:2017:K17-3} model was re-trained on the same
data as our system. Compared with UDPipe, we use an LSTM
instead of a GRU in our model and we also use a larger size for hidden units (64 vs.~20),
which has stronger representational power. 
Our bi-LSTM tokenizer achieves the best accuracy among all these
tokenizers.  These results speak to the value of statistical modeling
in tokenization for informal texts.%\nss{this paragraph needs copyediting}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
%		\hline
		\it System & Precision \\
		\hline
%		Stanford Postagger & 65.6 \\
		Stanford CoreNLP & 90.6 \\
%		UDPipe v1.2 & 78.7 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (greedy) & 93.7 \\
		\citealp{owoputi-EtAl:2013:NAACL-HLT} (CRF) & 94.6 \\
		\hdashline
%		UDPipe v1.2 & 83.8 \\
		\citealp{ma-hovy:2016:P16-1} & 92.5 \\
%		our word bi-LSTM & 89.2 \\
%		our character + word bi-LSTMs & 91.5 \\
%		\hline
	\end{tabular}
	\caption{POS tagger comparison on gold-standard tokens in the
          \textsc{Tweebank v2} test set.\nss{why Precision and not Accuracy?} \label{tbl:pos-result}}
\end{table}

\begin{table}[t]
	\centering
	\begin{tabular}{rc}
%		\hline
		\it Tokenization System & $F_1$ \\
		\hline
		Stanford CoreNLP & 92.3 \\
		our bi-LSTM tokenizer (\S\ref{sec:tok}) & 93.3 \\
%		\hline
	\end{tabular}
	\caption{\citet{owoputi-EtAl:2013:NAACL-HLT} POS tagging performance with automatic tokenization on
          the \textsc{Tweebank v2} test set. \label{tbl:pos-result-vs-tok}}
\end{table}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rccc}
%		\hline
		\it System & UAS & LAS & Kt/s \\
		\hline
		\citet{kong-EtAl:2014:EMNLP2014} & 81.4 & 76.9 & 0.3 \\
		\citet{dozat-qi-manning:2017:K17-3} & 81.8 & 77.7 & 1.7 \\
%		\newcite{dyer-EtAl:2015:ACL-IJCNLP} & 77.9 & 73.0 \\
		\newcite{ballesteros-EtAl:2016:EMNLP2016} & 80.2 & 75.7 & 2.3 \\
		\hdashline
		Ensemble (20) & 83.4 & 79.4 & 0.2 \\
		Distillation ($\alpha =1.0$) & 81.8 & 77.6 & 2.3 \\
		Distillation ($\alpha =0.9$) & 82.0 & 77.8 & 2.3 \\		
		Distillation w/ exploration & 82.1 & 77.9 & 2.3 \\
%		\hline
	\end{tabular}
	\caption{Dependency parser comparison on \textsc{Tweebank v2} test set,
           with automatic POS tags. The ``Kt/s'' column shows
           the parsing speed evaluated by thousands of tokens
           the model processed per second.
            \label{tbl:parse-result}}
\end{table}

@@

\begin{table}[t]
	\centering
	\begin{tabular}{rrcc}
%		\hline
		\it Pipeline stage & Score & Ours & SOTA \\
		\hline
		Tokenization  & \it $F_1$ & 98.3 & 97.3 \\		
		POS tagging &  \it  $F_1$ & 93.3 & 92.2 \\
		UD parsing & \it LAS $F_1$ & 74.0 & 71.4 \\
%		\hline
	\end{tabular}
	\caption{Evaluating our pipeline against a state-of-the-art pipeline.\label{tbl:pipline} %\yicomment{see tab5 for our tokenizer the pos tagging number is 93.6, here is 93.7, should be consistent}
	}
\end{table}
